Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
epiestim and OLS part of methodology:

[What methods/models are best]
[What condition(s) does each method/model work well/poorly]
[Conclusion about dataset]

### Posterior Estimates

@@

Fitting our Bayesian model, which extends the method of Thompson et. al, values
of beta were estimated for temperature, relative humidity, Gross Domestic
Product (GDP) and population density, respectively. The mean estimate of $\beta^T$ is

$$ \beta^T = [-0.23198507 -0.05391226  0.26336295 -0.03586852] $$

in the overall model for $R$:

Note that each feature's data is standardized to mean 0 and variance 1.

The model indicates that higher temperatures are observed with lower $R$ values,
and higher GDP is observed with higher $R$ values, while relative humidity and
population density have close to no effect on $R$. Because of the confidence
intervals, we are fairly confident of the directional correctness of this
relationship for temperature and for GDP per capita.

### Estimates of $\theta$, transformed to climate-independent $R$ by date

@@

$R$ is high in early phases, with an early spike on February 27, potentially due
to increases in testing, which means the data (and hence the model) has
underestimated the number of infectious cases compared to the ground truth.
This result is aggregate across the entire nation and is net of any contribution
to national weather changes.

@@

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot6.png}
\includegraphics[width=.49\textwidth]{plots/plot7.png}
\includegraphics[width=.49\textwidth]{plots/plot8.png}
\includegraphics[width=.49\textwidth]{plots/plot9.png}
\end{center}

These plots show the estimated $R$ values in each province computed through the
samples from the MCMC. An important observation is that the confidence intervals
for many provinces are very wide, because those provinces have relatively little
data. However, one strength of our model is that no weighting on results from
each province needs to be manually done. The data from larger provinces is
automatically more important because the Poisson likelihood function returns
smaller results as the rate parameter increases.

We have also analyzed the $\lambda$ and $\varepsilon$ parameters of the model,
but because these are not as important, see the Appendix for plots and analysis.

In many cities, our estimated $R_0$ values are extremely high. This is because
those cities reported a dramatic increase in cases, and our estimated $R_0$
values are indeed consistent with the data. However, we will discuss in the
interpretation section the limits of our approach, and why we believe this may
not match the ground truth.

@@

### Posterior of $\lambda$, location-dependent adjustment to $log(R)$

@@

$\lambda$ is an adjustment to the model based on the location. What we observe
from the distribution of $\lambda$ is that some locations have much more
certainty in how they deviate from the mean than others. This can be explained
by the unequal distribution of cases across provinces; provinces with more cases
lend themselves to more accurate estimation of $R$.

### Epsilon, idiosyncratic adjustment to log(R)

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot11.png}
\end{center}

This histogram shows all samples of all entries in the $\varepsilon$ matrix.
Generally, we prefer a lower average spread of $\varepsilon$, because it means
that more of the variation in reproduction number can be predicted from the
seasonal factors, location, and time alone. Unfortunately, we found the observed
spread of $\varepsilon$ is quite high, indicating that there is substantial
variance in reproductive numbers inferred from the data which cannot be
explained by modeled features.

>>>>

@@

[TK: Beta Values]
Fitting our Bayesian model, which extends the method of Thompson et. al, values of beta were estimated for temperature, relative humidity, Gross Domestic Product (GDP) and population density, respectively.  Thus, our model estimates $\beta^T = [,,,,]$ in
$$ R_i(t) = \exp\left( \theta(t) + \lambda_i + \mathbf{\beta}^T x_i(t) + \varepsilon_i(t) \right)$$
Note that each feature's data is standardized to mean 0 and variance 1.

The model indicates that higher temperatures are observed with lower $R_0$ values, and higher GDP is observed with higher $R_0$ values, while relative humidity and population density have $R_0$ close to zero.

### Climate-Independent Basic R, by Date

@@

First, we observe that our computed value of $R_0$ in Italy matches what We observe that R_0 spikes in , with an early spike on February 27, potentially due to increased in testing, which captures cases before.

@@

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot6.png}
\includegraphics[width=.49\textwidth]{plots/plot7.png}
\includegraphics[width=.49\textwidth]{plots/plot8.png}
\includegraphics[width=.49\textwidth]{plots/plot9.png}
\includegraphics[width=.49\textwidth]{plots/plot10.png}
\end{center}

Observe that in many cities, our estimated $R_0$ values are extremely high compared to the climate-independent plot shown earlier.

@@

### Posterior of Lambda, location-dependent adjustment to log(R)

@@

### Epsilon, Idiosyncratic adjustment to log(R)
\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot11.png}
\end{center}
